Spatial Analysis

### 2021-07-28 Scripts/spatial_analisis.Rmd
got port buffers

# ports_data <- my_path("D","NOAA", name = "SSmith_2015-2021 Landings_JUN 2021.xlsx", read = T) %>% 
#   slice(-50) %>% # remove uneccessary row
#

gfw_data <- my_path("D","Spatial",name = "gfw_portdata.csv", read = T) %>% 
  filter(iso3 == "USA")

@@

# Buffer state waters
state_bf = st_buffer(state_sf, 410000) %>% 
  st_transform(4326) %>% # to match shape
  st_set_crs(4326)

@@

@@

# Buffer state waters
state_bf = st_buffer(state_sf, 410000) %>% 
  st_transform(4326) %>% # to match shape
  st_set_crs(4326)

@@

@@

*Note:* Dark grey shaded area is the grid

@@

# Looks good
state_sf %>%
  st_transform(4326) %>% # to match shape
  st_set_crs(4326) %>%
  # st_simplify(preserveTopology = TRUE, dTolerance = 10000) %>%
  ggplot() +
  geom_sf(aes(color = state))+
  # geom_sf(data = eez_sf, aes(),fill =NA) +
  # ggplot()+
  geom_tile(data = ne_grid,
            aes(
              x = lon,
              y = lat
            ),
            alpha = 0.2
  ) +
  scale_color_manual(values = state_pallet) +
  theme_bw()+
  theme_dark()

@@

Once we have a gridded area, we converted the grid to a `sf` so we can merge it with the buffered states and finally filter out everything outside the states polygon

>>>>

# Get Global Fishig Watch data
gfw_data <- my_path("D","Spatial",name = "gfw_portdata.csv", read = T) %>% 
  filter(iso3 == "USA")

@@

# Buffer state waters
state_bf = st_buffer(state_sf, 4) %>% 
  st_transform(4326) %>% # to match shape
  st_set_crs(4326)

@@

We set a buffer of *4* deg (410 km, ~ 221 nm) that overshoots the EEZ a bit, but is eventually cropped

@@

# Buffer state waters
ports_bf = st_buffer(port_sf, 4) %>% 
  st_transform(4326) %>% # to match shape
  st_set_crs(4326)

@@

ggplot() +
  geom_sf(data = eez_sf, aes(),fill = NA) +
  geom_sf(data = ports_bf, aes(color = state), fill = NA) +
  scale_color_manual(values = state_pallet)+
  theme_dark()

@@

*Note:* Dark grey shaded area is the grid and is the same for both approaches

@@

# Looks good
state_sf %>%
  st_transform(4326) %>% # to match shape
  st_set_crs(4326) %>%
  # st_simplify(preserveTopology = TRUE, dTolerance = 10000) %>%
  ggplot() +
  geom_sf(aes(color = state))+
  # geom_sf(data = eez_sf, aes(),fill =NA) +
  # ggplot()+
  geom_tile(data = ne_grid,
            aes(
              x = lon,
              y = lat
            ),
            alpha = 0.2
  ) +
  scale_color_manual(values = state_pallet) +
  theme_bw() +
  theme_dark()

@@

Once we have a gridded area, we converted the grid to a `sf` so we can merge it with the buffered statesand ports and finally filter out everything outside the states polygon

###### 2.1.1 State Waters
